Augmentation of a Model Historical Harpsichord Mechanism for Haptic Enabled Interaction

### 2025-01-16 src/main.tex
Updates from Overleaf
abstract wording

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{The NIME of the Title Is Hello}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Matthew Hamilton}
% \authornote{Both authors contributed equally to this research.}
\email{matthew.hamilton2@unibo.it}
\orcid{1234-5678-9012}
\author{Michele Ducceschi}
% \authornotemark[1]
\email{michele.ducceschi@unibo.it}
\affiliation{%
  \institution{Università di Bologna}
  \city{Bologna}  
  \country{Italy}
}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Presented is a design for an electronically augmented replica of a 16th century
harpsichord interface, in the style of a Trasuntino from 1547. The interface was
designed, fabricated and exhibited in a collaboration between the NEMUS project
at the Università di Bologna and the Museo San Colombano, which hosts the
Tagliavini Collection of playable historical keyboard instruments. The interface
was commissioned as part of an exhibition and as a means of interacting with
items in the collection that are no longer in playing condition. The keyboard is
a replica of the mechanism found in harpsichords in the Trasuntino style, with
un-pitched strings under tension to provide a comparable mechanical resistance
as found on an original. A system of infra-red LED / phototransistor pairs were
connected to a microcontroller and installed inside the interface from which a
stream of data can be generated for each jack. The paper covers the design
criteria, process, open-source development and execution of installation for
exhibition at San Colombano.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
  Your, Paper}
%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{images/side_w-o_sensors.jpeg}
  \caption{3-key Model Harpsichord Mechanism by Graziano Bandini, Bologna 2023}
  \Description{3-key Model Harpsichord Mechanism by Graziano Bandini, Bologna 2023}
  \label{fig:teaser}
\end{teaserfigure}

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Augmentation of a Model Historical Harpsichord Mechanism for Haptic Enabled Interaction}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Matthew Hamilton}
% \authornote{Both authors contributed equally to this research.}
\email{matthew.hamilton2@unibo.it}
% \orcid{1234-5678-9012}
\author{Michele Ducceschi}
% \authornotemark[1]
\email{michele.ducceschi@unibo.it}
\affiliation{%
  \institution{Università di Bologna}
  \city{Bologna}  
  \country{Italy}
}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Presented is a design for an electronically augmented replica of a 16th century
harpsichord interface, in the style of a 1547 Trasuntino harpsichord. The
interface was designed, fabricated, and exhibited in a collaboration between the
NEMUS project at the Università di Bologna and the Museo San Colombano, which
hosts the Tagliavini Collection of playable historical keyboard instruments. The
interface was commissioned as part of an exhibition and as a means of
interacting with items in the collection that are no longer in playing
condition. The keyboard is a replica of the mechanism found in harpsichords in
the Trasuntino style, with un-pitched strings under tension to provide a
comparable mechanical resistance as found on an original. A system of infra-red
LED / phototransistor pairs was connected to a microcontroller and installed
inside the interface from which a stream of data can be generated for each jack.
The paper covers the design criteria, process, open source development, and
execution of installation for exhibition at San Colombano.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{interactive exhibit, augmented instrument, optical sensing, harpsichord}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{images/side_w-o_sensors.png}
  \caption{3-key Model Harpsichord Mechanism by Graziano Bandini, Bologna 2023}
  \Description{3-key Model Harpsichord Mechanism by Graziano Bandini, Bologna 2023}
  \label{fig:teaser}
\end{teaserfigure}
